A Linked Open Social Database for Scientific Benchmarking

### 2016-07-28 paper.tex
finished rendering tables
finished license issues

\input{tables/basicOverall}

@@

\section{Conclusions}
\label{conclusions}
The Linked Open Social Data (LOSD) presented in this article
should be available online in the \url{http://linkedopensocialdata.org}
address in near future to fulfill the purpose of being a common
repertoire in current research.
One should access \url{http://wiki.nosdigitais.teia.org.br/LOSD}
for reaching the address where LOSD is currently reachable.

\section*{References}
%
\bibliography{paper}
%\bibliography{myLastBibfile.bib}
%
\end{document}

>>>>

@@

\section{License issues}
% Facebook, Twitter, IRC, Gmane, Participa, CD, AA.
The database presented in this article is released under public domain.
Computer scripts are in public git repositories and PyPI Python packages.
Although most data is already in open licenses (Twitter, Email, Participabr,
Cidade Democrática, and AA data), IRC and Facebook data was collected
and donated by the individuals which yield the data.
This rises the the understanding of the right to study such data as the right to access the self,
in parity with anthropological endaviors~\cite{antphy,antphy2}.
% Of central importance to the obtainment of the data is the concept of
% anthropological physics~\cite{antphy}
\section{Conclusions}
\label{conclusions}
The Linked Open Social Data (LOSD) presented in this article
should be available online in the \url{http://linkedopensocialdata.org}
address in near future to fulfill the purpose of being a common
repertoire in current research.
One should access \url{http://wiki.nosdigitais.teia.org.br/LOSD}
for reaching the address where LOSD is currently reachable.

\section*{References}
%
\bibliographystyle{plainurl}
\bibliography{paper}
%\bibliography{myLastBibfile.bib}
%
\end{document}
